Growth of the South African Economy:\\An Empirical Evaluation

### 2014-07-22 Article_JAE_2014/ZAGrowth_JAE.Rnw

<<data, echo=FALSE, message=FALSE>>=
# Load historical data
historicalData <- Econ2011 # From the EconData package
historicalData <- subset(historicalData, subset=Country=="ZA")

>>>>

<<data, echo=FALSE, message=FALSE>>=
# Load historical data
historicalData <- subset(AllHistData, subset=Source=="Calvin2011" & Country=="ZA") # From the EconData package
# historicalData <- subset(historicalData, subset=Country=="ZA")
